The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-07 talk/vmil2012/paper.tex
comment in again
mention reviewers

All measurements presented in this section do not take garbage collection of resume data and machine code into account. Pieces
of machine code can be globally invalidated or just become cold again. In both
cases the generated machine code and the related data is garbage collected. The
figures show the total amount of operations that are evaluated by the JIT and
the total amount of code and resume data that is generated.
%The measurements and the evaluation focus on trace properties and memory
%consumption, and do not discuss the execution time of the benchmarks. These
%topics were covered in earlier work~\cite{bolz_allocation_2011} and furthermore
%are not influenced that much by the techniques described in this paper.

@@

\section*{Acknowledgements}
We would like to thank David Edelsohn, Samuele Pedroni, Stephan Zalewski and Sven Hager for their helpful
feedback and valuable comments while writing this paper.
We thank the PyPy and RPython community for their continuous support and work:
Armin Rigo, Antonio Cuni, Maciej Fijałkowski, Samuele Pedroni, and countless
others. Any remaining errors are our own.

>>>>

All measurements presented in this section do not take garbage collection of resume data and machine code into account. Pieces
of machine code can be globally invalidated or just become cold again. In both
cases the generated machine code and the related data is garbage collected. The
figures show the total amount of operations that are evaluated by the JIT and
the total amount of code and resume data that is generated.
The measurements and the evaluation focus on trace properties and memory
consumption, and do not discuss the execution time of the benchmarks. These
topics were covered in earlier work~\cite{bolz_allocation_2011} and furthermore
are not influenced that much by the techniques described in this paper.

@@

\section*{Acknowledgements}
We would like to thank David Edelsohn, Samuele Pedroni, Stephan Zalewski, Sven
Hager, and the anonymous reviewers for their helpful
feedback and valuable comments while writing this paper.
We thank the PyPy and RPython community for their continuous support and work:
Armin Rigo, Antonio Cuni, Maciej Fijałkowski, Samuele Pedroni, and countless
others. Any remaining errors are our own.
